Legends for supplementary material

### 2020-01-08 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

**Supplementary Table 1. Hi-C data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.

**Supplementary Table 2. Genomic annotations.** A complete list of the genomic annotations used to build the feature space for all downstream models. The GRCh37/hg19 human genome assembly was used. "Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Available Cell Type" - the name of the cell type in which the annotation was available, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).

>>>>

**Supplementary Table 1. Hi-C data.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains.

**Supplementary Table 2. Genomic annotations.** A complete list of the genomic annotations used to build the feature space for all downstream models. The GRCh37/hg19 human genome assembly was used. "Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
